Extended Data

### 2021-04-27 doc/manuscript/Dow_Extended_Data.Rmd
clean up

---
title: "Extended Data"
author:
output: 
  pdf_document:
    fig_caption: yes
    #toc: true # table of content true
    #toc_depth: 2  
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---
```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
path_to_results <- paste0(dirname(dirname(getwd())), "/results/") #I was trying to read directly from results folder, but couldn't get it working.

@@

```{r growth_curves_all, out.width="100%", echo=FALSE, fig.align="center", fig.cap= growth_curves_all_caption, fig.pos="H", warning=FALSE}
knitr::include_graphics("tables_figures/growth_curves_all.png")
```

\newpage
```{r climwin, out.width="70%", echo=FALSE, fig.align="center", fig.cap= climwin_caption, warning=FALSE}
knitr::include_graphics("tables_figures/climwin_figure.png")
```

\newpage
```{r tree_rings_TMIN, out.width="120%", echo=FALSE, fig.align="center", fig.cap= tree_rings_TMIN_short_caption, warning=FALSE}
knitr::include_graphics("tables_figures/tree_rings_tmin.png")
```

>>>>

---
title: ""
author:
output: 
  pdf_document:
    fig_caption: yes
    #toc: true # table of content true
    #toc_depth: 2  
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---
```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
path_to_results <- paste0(dirname(dirname(getwd())), "/results/") #I was trying to read directly from results folder, but couldn't get it working.

@@

![`r growth_curves_all_caption`](tables_figures/growth_curves_all.png){ width=100% }

![`r climwin_caption`](tables_figures/climwin_figure.png){ width=70% }

![`r tree_rings_TMIN_short_caption`](tables_figures/tree_rings_tmin.png){ width=90% }
